Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-24 Manuscript/sec4-experiments.tex
fix transferring

To find out the performance bottleneck with the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on CPU, \emph{transfering} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
\figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
For the neighbor sampler, the sampling technique reduced the training time per batch only when the batch size was very small.
When the batch became bigger, the sampling and the data transferring phases introduced noticeable overheads, even making the training time exceed the full-batch training.
For the clustering sampler, the sampled subgraph was smaller than the neighbor sampler under the same relative batch size.
The reduction in the training time was more obvious than the neighbor sampler.
However, the overheads increased quickly as the relative batch size increased.
The training time under the 25\% relative batch size already exceeded the time of full-batch training.
The experimental results indicate that the implementation of the sampling techniques in PyG is inefficient.
When the batch size was slightly big, more than 50\% of the time had been spent on sampling and data transferring.
\emph{The sampling techniques are only efficient under small batch sizes.}

>>>>

To find out the performance bottleneck with the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on CPU, \emph{transferring} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
\figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
For the neighbor sampler, the sampling technique reduced the training time per batch only when the batch size was very small.
When the batch became bigger, the sampling and the data transferring phases introduced noticeable overheads, even making the training time exceed the full-batch training.
For the clustering sampler, the sampled subgraph was smaller than the neighbor sampler under the same relative batch size.
The reduction in the training time was more obvious than the neighbor sampler.
However, the overheads increased quickly as the relative batch size increased.
The training time under the 25\% relative batch size already exceeded the time of full-batch training.
The experimental results indicate that the implementation of the sampling techniques in PyG is inefficient.
When the batch size was slightly big, more than 50\% of the time had been spent on sampling and data transferring.
\emph{The sampling techniques are only efficient under small batch sizes.}
